Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-13 ms.tex
clean-up of low-frequency predictions section, added sentence about superiority of two-component emission predicts to conclusions section

All of the best-fit offsets, in both the single-MBB and two-component cases,
are within the uncertainties quoted in Table \ref{table:offs}. On the other 
hand, Figure \ref{fig:lofreq} shows that the \cite{planckdust} single-MBB 
predictions yield slopes substantially different from unity: 1.079 at 217 GHz, 
1.126 at 143 GHz, and 1.188 at 100 GHz. The fact that the slopes are larger 
than unity indicates that the \cite{planckdust} predictions are systematically 
low. The systematic underprediction evidently become gradually more severe as 
lower frequencies are considered, with a 7.9\% underprediction at 217 GHz, a 
12.6\% underprediction at 143 GHz and an 18.8\% underprediction at 100 GHz.

For the case of the two-component model, we perform full-resolution 217-3000 
GHz fits using the \PLANCK+DIRBE favored global parameters (Table 
\ref{tab:global}, model 2), then smooth to $1^{\circ}$ FWHM and bin down to 
$N_{side}=64$ before predicting the 100-217 GHz emission. The bottom row of
Figure 14 shows that each of the best-fit lines is very similar to the 
corresponding red line which represents a perfect match between predicted and 
observed emission. More quantitatively, the two-component slopes are all within
2.2\% of unity: 0.978 at 217 GHz, 0.986 at 143 GHz and 1.022 at 100 GHz. 
We note that at 217 GHz, the good agreement is in some sense predetermined by 
the fact that \PLANCK~217 GHz has been included in our two-component MCMC fits.
On the other hand, the 143 and 100 GHz predictions are truly based on 
extrapolation.

@@

Nevertheless, we have established that the two-component emission model
remains viable in light of the \PLANCK~HFI data, and that the FIR/submm 
dust SED's preference for two MBB components rather than just one is not
simply an idiosyncracy of the FIRAS spectra. We recommend that those interested
in thermal dust foregrounds in the 100-3000 GHz frequency range use our data 
release to predict unpolarized dust emission, at the very least in order to 
help determine the level at which the choice of dust emission model may 
influence their conclusions.
%last sentence needs work

>>>>

In both the single-MBB and two-component cases, all of the best fit offsets
are within the uncertainties quoted in Table \ref{table:offs}. On the other 
hand, the top row of Figure \ref{fig:lofreq} shows that the \cite{planckdust} 
single-MBB predictions yield slopes substantially different from unity: 1.079 
at 217 GHz, 1.126 at 143 GHz, and 1.188 at 100 GHz. The fact that the slopes 
are larger than unity indicates that the \cite{planckdust} predictions are 
systematically low. The systematic underprediction evidently become gradually 
more severe as lower frequencies are considered, with a 7.9\% underprediction 
at 217 GHz, a 12.6\% underprediction at 143 GHz and an 18.8\% underprediction 
at 100 GHz.

For the case of the two-component model, we perform full-resolution 217-3000 
GHz fits using the \PLANCK+DIRBE favored global parameters (Table 
\ref{tab:global}, model 2), then smooth to $1^{\circ}$ FWHM and bin down to 
$N_{side}=64$ before predicting the 100-217 GHz emission. The bottom row of
Figure 14 shows that each of the best-fit lines is very similar to the 
corresponding red line which represents a perfect match between predicted and 
observed emission. More quantitatively, the two-component slopes are all within
2.2\% of unity: 0.978 at 217 GHz, 0.986 at 143 GHz and 1.022 at 100 GHz. 
We note that at 217 GHz, the good agreement is in some sense predetermined by 
the fact that \PLANCK~217 GHz has been included in our two-component MCMC fits.
On the other hand, the 143 and 100 GHz predictions are based on extrapolation.

We conclude from our predicted versus observed emission comparison that our 
two-component model outperforms the \cite{planckdust} single-MBB model at 
predicting Galactic thermal dust emission in diffuse regions from 100-217 GHz.

% could add a last sentence trying to soften this, acknowledging that 
% planck team warned about their model below 353 GHz

@@

Nevertheless, we have established that the two-component emission model
remains viable in light of the \PLANCK~HFI data, and that the FIR/submm 
dust SED's preference for two MBB components rather than just one is not
simply an idiosyncracy of the FIRAS spectra. Furthermore, we showed in 
$\S$\ref{sec:lofreq} that our 100-217 GHz two-component emission predictions
are more accurate than those of \cite{planckdust} by margins of $\sim$5-15\%.
We therefore recommend that those interested in thermal dust foregrounds in 
the 100-3000 GHz frequency range use our data release to predict unpolarized 
dust emission, at the very least in order to help determine the level at which 
the choice of dust emission model may influence their conclusions.
%last sentence needs work
